Modeling the impacts of replacing car trips with combined public transport and cycling: \ Reproducible methods, results and actionable evidence from the biclaR project

### 2023-11-28 paper/PaperCEUS/PaperCEUS.Rmd
Clarify results

Table \ref{tab:summary22} presents the results of the avoided emissions and its monetization for the second leg of the journey, by replacing car trips with potential TP trips.  
Regarding the PT segment, the shift from private car would lead to the mitigation of CO~2~ equivalent emissions to 8,500 to 20,800 tons annually, valued in €1.4 million to €3.5 million yearly.

>>>>

Table \ref{tab:summary22} presents emissions reductions and associated economic benefits associated with the second (PT) leg of trips.
The shift from private car associated with thes PT segments would reduce CO~2~ equivalent emissions by 8,500 to 20,800 tons annually, valued in €1.4 million to €3.5 million yearly, for the 4% and 10% targets, respectively.
